Search-based Synthesis of Network Intrusion Detection Rules

### 2019-09-23 paper/paper.tex
pass on intro

\sloppy \nids{} are typically categorized in two
groups~\cite{kumar2007survey}: 1)~rule-based and 2)~anomaly-based. A
rule-based \nids{} (\aka\ signature-based NIDS) checks if the network
traffic matches a fixed set of
rules. Figure~\ref{fig:synflood-example} shows an example rule of
Suricata~\cite{suricata}, a popular open-source \nids{}. This rule
prescribes a method to capture a denial-of-service attack to a
server~\cite{Douligeris:2004:DAD:987153.987158}. Rule-based \nids{} focuses on known attacks whereas
anomaly-based \nids{} focuses on unanticipated attacks that could be
observed through suspicious network
traffic~\cite{kumar2007survey,Mitchell:2014:SID:2597757.2542049,cordy-etal-issta19}.

These intrusion detection mechanisms are complementary. Rule-based
NIDS are very popular in industry (it is clear to system
administrators what rules will do), but attacker are creating in
evading the current set of rules, and writing these rules is tedious
and error-prone. Anomaly-based NIDS are not restricted to a fixed set
of rules; they learn common behaviors and dynamically detect uncommon
behavior. The often use some machine learning algorithm to model
sequence of events~\cite{7579764}. Unfortunately, anomaly-based NIDS
can raise false alarms as behavior models are fundamentally
imprecise. To sum up, both approaches have positive and negative
aspects.

>>>>

\sloppy \nids{} are typically categorized in two
groups~\cite{kumar2007survey}: 1)~rule-based and 2)~anomaly-based. A
rule-based \nids{} (\aka\ signature-based NIDS) checks if the network
traffic matches a fixed set of
rules. Figure~\ref{fig:synflood-example} shows an example rule of
Suricata~\cite{suricata}, a popular open-source \nids{}. This rule
prescribes a method to capture a denial-of-service attack to a
server~\cite{Douligeris:2004:DAD:987153.987158}. Rule-based \nids{} focus on known attacks whereas
anomaly-based \nids{} focus on unanticipated attacks that could be
observed through suspicious network
traffic~\cite{kumar2007survey,Mitchell:2014:SID:2597757.2542049,cordy-etal-issta19}.

These intrusion detection mechanisms are complementary. Rule-based
NIDS are restricted to a fixed set of rules and not all rules are
simulneteously enabled (for efficiency). Attackers constantly create
new attacks, and manually writing rules is tedious and
error-prone. However, the semantics of the specification language of
rules is clear making it easy for system administrator to understand
them. As such, rule-based systems are very popular in industry.
Anomaly-based NIDS are not restricted to a fixed set of rules; they
learn common behaviors and dynamically detect uncommon behavior. They
typically use machine learning algorithm to model event
sequences~\cite{7579764}. Unfortunately, anomaly-based NIDS can raise
false alarms as behavior models are fundamentally imprecise. To sum
up, both approaches have positive and negative aspects.
